### 2015-02-22 Workshop2015/incremental.tex
Figures and general organization
Incremental & Use Case

We propose an SLA guided, continuous data provision and integration approach that consists in three steps  starting from the processing of the query  to the delivery of the results.
Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system. It accesses data services which are data providers deployed in a cloud  that provide agreed SLA’s. 
Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, execution time, the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results, delivering adata and launching and re-launching queries. Intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process. 
%The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.

@@

\begin{figure*}
\includegraphics[width=0.99\textwidth]{arch.png}
\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
\end{figure*}

In order to illustrate our approach, consider a smart city that aims at being energy self-sustainable and produce and consume, as much as possible, energy within its geographic area. 
Producers are characterized according to their location, the amount of energy in Kilowatts-hour that they can sell, the cost of that energy, and the time window in which they can produce it. 
Consumers are described by their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy. 
An energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.

@@

In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers. 
Each of them is specified by a clause:
\begin{trivlist}\sf\footnotesize
\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
\end{trivlist}

@@

According to our approach, energy producers are modelled as data services with associated ``agreed'' SLAs. In the example, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
Assume that there are four household energy providers that can be queried individually and two hubs that collect information from the community smartmeters.
Hubs will store information about (surplus) energy, available from particular users.
We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$ and h$_2$}.
We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates. 
All these services can potentially be combined for answering queries.

An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.

Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
For instance, \textit{List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt and that are labeled as green?}. 
The user preferences statement would include their cloud provider contract and quality preferences:

@@

We assume that services export SLAs (i.e., agreed SLAs) that define measures   that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associted to services, and hybrid they can be statically stated  but they change at execution time.  A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}). The service SLA measures  that we consider are: response time, availability, price/call, reliability, data production rate. Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.

An example of computed measure is the cost of retrieving the list of energy providers within a region with their KWatt cost. The cost is determined by the  cost of the calls. This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network.

@@

In the example, some of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query. These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
\begin{trivlist}\sf\footnotesize
\item[~$\bullet$ ] query total cost: $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$5
 \item[~$\bullet$ ] total response time: of services + data transfer
 \item[~$\bullet$ ] availability: {\em (of services involved)} $\leq$ {\sf 90$\%$}, 
 \item[~$\bullet$ ] freshness: non 
 \item[~$\bullet$ ] precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
 \item[~$\bullet$ ] provenance:  all services involved must be $green$
 \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1$ GB
 \end{trivlist}

Therefore, we propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements. It specifies also how to compute coarse grained measures with fine grained ones. For example, data precision will be computed as a function of availability, freshness and provenance exported by data services. The derived SLA  can be seen as a set of inequations that have to be solved during the execution of a service composition. Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated. We will discuss this issue in the next sections.

@@

\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
Let us consider the case of the smart city scenario, where particulars can participate on an energy trading pool.
We suppose that this hypothetical city has a large number of households that sell their energy surplus to other consumers. 
The city has four information hubs, located in four different neighborhoods, connected to very small energy producers.
Other producers are be contacted directly, though the services of three different cloud providers.
Each cloud provider exports its own interfaces.
 SLAs are defined for each individual energy provider server, each hub, and each cloud provider.

When an on-line consumer searches  servers to buy energy, a composed web service is generated, in order to fetch each individual or hub service and to start  energy reservation procedures.
Depending on the location of the consumer and producers, different conditions and constraints may apply.
Also  cloud providers  publish the conditions for using their services.
These conditions are expressed as user preferences and SLAs.
Additionally, other non-functional requirements (such as authentication or security requirements) may apply.

In this context, the user  expresses an energy order, her location and payment information. A composite web service is  generated to fulfil the order.
The generated service composition should consider the nearest providers, in accordance to the agreed SLA.

In order to produce a personalised service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
The specification of each available service is also considered (this specification should be given by the service provider).
~\hfill\openbox
\end{example}

Given a a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
Some of the unequations of the derived SLA should be included in the service compositions that answer the query.
In the case of our query example the following composition can be used for answering it:
\begin{eqnarray*}
Q_1 &\equiv&
   \langle X_1,Y_1\rangle = loc_1(IP), \\
&& \langle X_2,Y_2 \rangle = loc_1(Eprovider), \\
&& D = distance(\langle X_1,Y_1\rangle, \langle X_2,Y_2\rangle), \\
&& \langle C_1, E_1 \rangle = e_1(\dots), \dots \langle C_4, E_4 \rangle = e_4(\dots), \\
&& D \leq 1.5 \mathsf{Km},\ \ sum(C_1:C_4) \leq 5, \\
&& sum(E_1:E_4) \geq 1000\ \mathsf{kw-h}, \\
&& \mathsf{totalResponseTime}  \leq 10\ \mathsf{seg}
\end{eqnarray*}

@@

\begin{example}[Incremental queries]\label{Ex:rew2}
Let us return to the energy trade system of Example~\ref{Ex:rew1}.
 Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{One MegaWatt-hour}''.
In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the one MegaWatt-hour capacity is reached.
Let us suppose that, in order to minimize the the communications between servers, the lists need to be produced incrementally.
In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the desired capacity.

@@

%-----------------------------------------------------------------
\section{Dealing with the resources consumed by the evaluation process}
\label{sec:queryProcessOpt}
%-----------------------------------------------------------------
 Our data provision and integration approach relys on data services deployed on one or different providers and it is delivered as a DaaS. This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be invested in a query evaluation process. It is thus important to optimize the use of these resources.

@@

Second, precalculated queries and partial results can be also stored in cache or in a persistent supprt. Rewritting results can be also stored and reduce execution and resources consumption time when evaluating similar queries. Storing or not such SLAs will depend on the cloud subscription of the user the issued the query (data access, intermediate storage capacity , cost of storage , etc ... ).

As discussed in previous sections, the derived SLA associated to service compositions can have free measures that can only be evaluated at run-time. In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transfered when services deliver results. These computations are used dynamically for instanciating free variables in the derived SLA and thus determine wether te contract is respected by the execution of a query. Since this is monitered dynamicalle, the evaluation of the query can be adapted if the SLA is not being respected anymore.

>>>>

We propose an SLA guided, continuous data provision and integration approach that consists in three steps  starting from the processing of the query  to the delivery of the results.
Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system. It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, execution time, the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results, delivering adata and launching and re-launching queries. Intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process. 
%The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.

@@

\begin{figure*}
\center{
\includegraphics[width=0.75\textwidth]{arch.png}
\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}}
\end{figure*}

In order to illustrate our approach, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants. 
Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g. cost, inscription, or exchange unit), and the time window in which they can produce it. 
Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content. 
An energy exchange market is established in order to continuously trade  content provision/consumption ensuring that all consumers will have the content they require at every moment.

@@

In our example assume that there are several content provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several content providers. 
Each of them is specified by a clause:
\begin{trivlist}\sf\footnotesize
\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(Type, Cost, Size, location), \textit{SLA}$_i$
\end{trivlist}

@@

According to our approach, content producers are modelled as data services with associated ``agreed'' SLAs. In the example, we assume that several producers will be able to supply equivalent content for a given period of time given specific  preferences expressed by a consumer. 
Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
Hubs will store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$ and h$_2$}.
We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates. 
All these services can potentially be combined for answering queries.

A content request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.

Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
For instance, \textit{List of English poetry content providers that can provision commented Emily Dickinson poems, in the next hour, that are close to my city that are free and that are labeled as experts?}. 
The user preferences statement would include their cloud provider contract and quality preferences:

@@

We assume that services export SLAs (i.e., agreed SLAs) that define measures   that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.  A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}). The service SLA measures  that we consider are: response time, availability, price/call, reliability, data production rate. Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.

An example of computed measure is the cost of retrieving the list of "expert" Emily Dickinson poems providers within a region with their cost. The cost is determined by the  cost of the calls. This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaOctets through the network and the type of subscription of the user for using the network.

@@

In the example, some of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query. These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
\begin{trivlist}\sf\footnotesize
\item[~$\bullet$ ] query total cost: $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$5
 \item[~$\bullet$ ] total response time: of services + data transfer
 \item[~$\bullet$ ] availability: {\em (of services involved)} $\leq$ {\sf 90$\%$}, 
 \item[~$\bullet$ ] freshness: non 
 \item[~$\bullet$ ] precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
 \item[~$\bullet$ ] provenance:  all services involved must be $expert$
 \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1$ GB
 \end{trivlist}

Therefore, we propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements. It specifies also how to compute coarse grained measures with fine grained ones. For example, data precision will be computed as a function of availability, freshness and provenance exported by data services. The derived SLA  can be seen as a set of unequations that have to be solved during the execution of a service composition. Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated. We will discuss this issue in the next sections.

@@

\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
Let us consider the case of the MOOC scenario, where people can participate on an content trading pool.
We suppose that this hypothetical MOOC has a large number of participants that sell their content  to other consumers. 
The MOOC has four information hubs, located in four different geographic locations, connected to other content providers.
Other content providers are  contacted directly, through the services of three different cloud providers.
Each cloud provider exports its own interfaces.
 SLAs are defined for each individual content provider server, each hub, and each cloud provider.

When an on-line consumer searches  servers to buy/retrieve content, a composed web service is generated, in order to fetch each individual or hub service and to start  content retrieval procedures.
Depending on the location of the consumer and producers, different conditions and constraints may apply.
Also  cloud providers  publish the conditions for using their services.
These conditions are expressed as user preferences and SLAs.
Additionally, other non-functional requirements (such as authentication or security requirements) may apply.

In this context, the user  expresses a content order, her location and payment information. A composite web service is  generated to fulfill the order.
The generated service composition should consider the nearest providers, in accordance to the agreed SLA.

In order to produce a personalized service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
The specification of each available service is also considered (this specification should be given by the service provider).
~\hfill\openbox
\end{example}

Given a a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
Some of the un-equations of the derived SLA should be included in the service compositions that answer the query.
In the case of our query example the following composition can be used for answering it:
\begin{eqnarray*}
Q_1 &\equiv&
   \langle X_1,Y_1\rangle = loc_1(IP), \\
&& \langle X_2,Y_2 \rangle = loc_1(Cprovider), \\
&& D = distance(\langle X_1,Y_1\rangle, \langle X_2,Y_2\rangle), \\
&& \langle C_1, E_1 \rangle = e_1(\dots), \dots \langle C_4, E_4 \rangle = e_4(\dots), \\
&& D \leq 1.5 \mathsf{Km},\ \ sum(C_1:C_4) \leq 5, \\
&& union(E_1:E_4) \geq 5\ \mathsf{Go}, \\
&& \mathsf{totalResponseTime}  \leq 10\ \mathsf{seg}
\end{eqnarray*}

@@

\begin{example}[Incremental queries]\label{Ex:rew2}
Let us return to the energy trade system of Example~\ref{Ex:rew1}.
 Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson peotry.
In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the 5Go  capacity is reached.
Let us suppose that, in order to minimize the the communications between servers, the lists need to be produced incrementally.
In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the desired capacity.

@@

%-----------------------------------------------------------------
\section{Dealing with the resources consumed by the evaluation process}
\label{sec:queryProcessOpt}
%-----------------------------------------------------------------
 Our data provision and integration approach relies on data services deployed on one or different providers and it is delivered as a DaaS. This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be invested in a query evaluation process. It is thus important to optimize the use of these resources.

@@

Second, precalculated queries and partial results can be also stored in cache or in a persistent support. Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries. Storing or not such SLAs will depend on the cloud subscription of the user the issued the query (data access, intermediate storage capacity , cost of storage , etc ... ).

As discussed in previous sections, the derived SLA associated to service compositions can have free measures that can only be evaluated at run-time. In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transferred when services deliver results. These computations are used dynamically for instantiating free variables in the derived SLA and thus determine wether te contract is respected by the execution of a query. Since this is monitored dynamically, the evaluation of the query can be adapted if the SLA is not being respected anymore.

### 2015-02-22 Workshop2015/useCase.tex
Figures and general organization
Incremental & Use Case

Consider a smart city that aims at being energy self-sustainable and produce and consume, as much as possible, energy within its geographic area. 
Producers are characterized according to their location, the amount of energy in Kilowatts-hour that they can sell, the cost of that energy, and the time window in which they can produce it, with a given service level agreement concerning their availability and fault tolerance. 
Consumers are described by their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy. 
An energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.

In our approach, energy producers are modelled as services with associated ``agreed'' SLAs. 
In general, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers. 
In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers. 
Each of them is specified by a clause:
\begin{trivlist}\sf\footnotesize
\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
\end{trivlist}

Services are deployed in different cloud providers and each service exports an agreed SLA that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data. 
As said in previous sections, some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.  
Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data centre or between data centres ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}). For example some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g. zone 1 is Europe). If the customer wishes to deploy services in zone 1 but store data in zone 2 the transfer cost will change.

\begin{trivlist}\sf\footnotesize
\item[~$\bullet$ ] {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.

 \item[~$\bullet$ ]  {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}. 
 \end{trivlist}

Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
For instance, \textit{List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt and that are labeled as green?}. 
The user preferences statement would include their cloud provider contract and quality preferences:

\begin{trivlist}\sf\footnotesize
\item[~$\bullet$ ]  {\sf cloudSLA:$\langle$0,05 cents per call, 8 Gigabytes I/0 volume/month, free, 1 Giga$\rangle$}. 
\item[~$\bullet$ ] {\sf preferencesStatement:$\langle$query total cost,  total responseTime, reliability, freshness, precision, provenance, storage$\rangle$}. 
\end{trivlist}

We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}. 
The user is ready to pay maximum {\sf \$5 as total query cost}; she requests that only {\sf green} energy providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} and with a response time of {\sf 0,01 seconds}.

Assume that there are four household energy providers that can be queried individually and two hubs that collect information from the community smartmeters.
Hubs will store information about (surplus) energy, available from particular users.
We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$ and h$_2$}.
We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates. 
All these services can potentially be combined for answering the query.

 %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
 \paragraph{Derived SLA} 
 %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
 Some of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query. These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
\begin{trivlist}\sf\footnotesize
\item[~$\bullet$ ] query total cost: $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$5
 \item[~$\bullet$ ] total response time: of services + data transfer
 \item[~$\bullet$ ] availability: {\em (of services involved)} $\leq$ {\sf 90$\%$}, 
 \item[~$\bullet$ ] freshness: non 
 \item[~$\bullet$ ] precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
 \item[~$\bullet$ ] provenance:  all services involved must be $green$
 \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1 Giga$ 
 \end{trivlist}

%...---... ...---... ...---... ...---... ...---... ...---... ...---... ...---... ...---... 
  \paragraph{Computing service compositions} 
%...---... ...---... ...---... ...---... ...---... ...---... ...---... ...---... ...---...

Given a a set of services that can possibly be composed and the derived SLA, a service cmposition must be produced.
Some of the inequations of the derived SLA should be included in the service compositions that answer the query.
In the case of our query example the following composition can be used for answering it:
\begin{eqnarray*}
Q_1 &\equiv&
   \langle X_1,Y_1\rangle = loc_1(IP), \\
&& \langle X_2,Y_2 \rangle = loc_1(Eprovider), \\
&& D = distance(\langle X_1,Y_1\rangle, \langle X_2,Y_2\rangle), \\
&& \langle C_1, E_1 \rangle = e_1(\dots), \dots \langle C_4, E_4 \rangle = e_4(\dots), \\
&& D \leq 1.5 \mathsf{Km},\ \ sum(C_1:C_4) \leq 5, \\
&& sum(E_1:E_4) \geq 1000\ \mathsf{kw-h}, \\
&& \mathsf{totalResponseTime}  \leq 10\ \mathsf{seg}
\end{eqnarray*}

  In fact our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derived SLA are verified. 
One challenge of this is to generate incremental queries.

%.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  
\paragraph{Optimizing service compositions execution} 
%.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  .     
A service composition (expressed in a Datalog-like syntax) is then transformed into a query workflow search space consisting of workflows with different control flows and where constraints serve to determine an optimization objective. 
In the case of $Q_1$ above, the corresponding search space contains for example a workflow {\sf QW$_1$} where all activities are executed sequentially. 
Another one, {\sf QW$_2$}, with parallel activities programming the call to a location service for the user and the energy providers, then a filter activity selecting only services located not farther to 1.5 Km, followed by  parallel activities that compute the total cost of the energy to buy, the total amount of energy.

    Once the search space has been computed the QWs are filtered according to their economic and execution time costs. The QWs that minimize this cost are identified and ordered according to their conformance to the user preferences statement.

% \begin{figure*}
%\includegraphics[width=0.95\textwidth]{figs/exchange.pdf}
%\caption{\label{fig:energyXChange} Energy exchange.}
%\end{figure*}

>>>>

\begin{figure*}
\center{
\includegraphics[width=0.65\textwidth]{use-case.png}
\caption{General distributed data storage service.\label{fig:storage}}}
\end{figure*}

According to our example scenario, we conducted an experimental experience for implementing our data integration approach on a multi-cloud environment. We focussed on the implementation of a data as a service layer that integrates content from different services related to education but also related on data producers and consumers. Figure \ref{fig:storage} shows the general architecture of our scenario, deployed on Window Azure data store services and on Jelastic (https://jelastic.com), an open free cloud provider where we installed NE4J and Mongo NoSQL stores. The multi-cloud data as a service layer is a data provision platform storing clean data sets stemming from public data services (Linked in, Tweeter, Facebook) accessible on Internet and also from private ones.

The DaaS platform interacts recurrently with services in order to retrieve data and build collections that can be accessed by consumers. Each data service is characterized by the quality of data it provides, its availability and also by privacy and data ownership contrats provided as SLA contracts and enforced by security protocols.
